Gompertzian growth as infinitely correlated non-local growth

### 2023-08-05 arxiv2/new_draft.tex
fix

 The emergence of Gompertz growth from higher order logistic growth can be seen as another way to encode non-linear effects that were seen as coherence in accordance with Petroni and Molski. In practice, the augmented logistic model has a faster growth rate decay than the familiar $\theta$-logistic growth \ref{fig:hypergeometric_plain}. If we interpret speed of relative growth decay as coherence, the augmented logistic model would be more coherent than the $\theta$-logistic model for a given starting value.

>>>>

 The emergence of Gompertz growth from higher order logistic growth can be seen as another way to encode non-linear effects that were seen as coherence in accordance with Petroni and Molski. In practice, the augmented logistic model has a faster growth rate decay than the familiar $\theta$-logistic growth (Figure \ref{fig:hypergeometric_plain}). If we interpret speed of relative growth decay as coherence, the augmented logistic model would be more coherent than the $\theta$-logistic model for a given starting value.
